Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2019-01-11 scagnostics.Rmd

A large number of projection pursuit indexes have been developed, primarily based on departure from normality, which includes clusters or outliers, and also for finding separations between known groups (e.g. @f87, @CBC92, @lckl2005, @AHC02, @CEM:CEM2568, @JS87, @5508437).  Less work has been done on indexes to find nonlinear dependence between variables, when $d>1$.

>>>>

A large number of projection pursuit indexes have been developed, primarily based on departure from normality, which includes clusters, outliers and skewness, and also for finding separations between known groups (e.g. @f87, @hall89 @CBC92, @naito1997, @lckl2005, @AHC02, @CEM:CEM2568, @JS87, @5508437, @PAN2000153, @FER13, @LOPERFIDO201842).  Less work has been done on indexes to find nonlinear dependence between variables, when $d>1$.
